Evolution of ORM Systems: Formal Foundations

### 2013-01-17 doc/description.tex
fixes adding association

\textbf{TODO: define the features of the $f_m$ function}
\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = application(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = database(s) \bullet insertAssoc(l, a, f_m)
\end{align*}
The $insertAssoc$ function is defined as:
\begin{align*}
insertAssoc : Association \times Database \times (Row \times Row) \\
insertAssoc(l, a, f_m, d) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l\\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
addForeignKey(name(t_s), \rho(a,d), d) \\ \bullet \forall r \in f_m(l, reference(a)) : \\ insertRow(row(name(t_s), [name(a), \\ value(primaryKey(first(r)))]), d)
\end{gathered}
 }
 \\ \\
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) \\ startCardinality(a) > 1}{\begin{gathered} addTable(\rho(a,d),d) \\ \bullet \forall r \in f_m(l, reference(a)),\\ t \in tables(d) : name(t) = name(a) : \\ insertRow(row(name(a), [name(t_s), \\ value(primaryKey(first(r)))] [name(t_t), \\ value(primaryKey(second(r)))]), d)
\end{gathered}
 } 
 \end{cases}\\
 a \in Associations, d \lhd Database
\end{align*}

>>>>

\textbf{TODO: define the features of the $f_m$ function}
\begin{align*}
\mathbf{addAsociation} : Label \times Association \times (Row \times Row) \times State \rightarrow State \\
\Psi(s, addAsociation(l, a, f_m)) = application(s) \circ addAssoc(l, a) \\
\Phi(s, addAsociation(l, a, f_m)) = \begin{cases}
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l\\ 		\wedge name(t_t) = reference(a) \\ \wedge \forall f \in foreignKeys(t_t) \cuo columns(t_t) : name(f) \neq name(a) \\ startCardinality(a) \leq 1}{\begin{gathered}
		database(s) \bullet addForeignKey(name(t_s), \rho(a,d), d) \\ \bullet \forall r \in f_m(l, reference(a)) : \\ insertRow(row(name(t_s), [name(a), \\ value(primaryKey(first(r)))]), d)
	\end{gathered}}
 \\ \\
	\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = l \\ \wedge name(t_t) = reference(a) \\ \wedge startCardinality(a) > 1}{\begin{gathered} 
	database(s) \bullet addTable(\rho(a,d),d) \\ \bullet \forall r \in f_m(l, reference(a)) :\\ insertRow(row(name(owningClass(a)) + name(a), \\ [name(t_s), value(primaryKey(first(r)))]\\ [name(t_t), value(primaryKey(second(r)))]))
	\end{gathered}} 
\end{cases}\\
\end{align*}
